---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ```rda```: Shrunken Centroids Regularized Discriminant Analysis

<!-- badges: start -->
[![CRAN version](https://www.r-pkg.org/badges/version/rda)](https://cran.r-project.org/package=rda)
[![R-CMD-check](https://github.com/valentint/rda/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/valentint/rda/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/valentint/rda/branch/main/graph/badge.svg)](https://app.codecov.io/gh/valentint/rda?branch=main)
[![downloads](https://cranlogs.r-pkg.org/badges/rda)](https://cran.r-project.org/package=rda)
[![downloads](https://cranlogs.r-pkg.org/badges/grand-total/rda)](https://cran.r-project.org/package=rda)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
<!-- badges: end -->


## Installation

The ``rda`` package was removed from CRAN (The Comprehensive R Archive Network) and is currently archived. As soon as it is back on CRAN, we will inform you that it is possible to install it from CRAN:

    ##    install.packages("rda")

## Building from source

To install the latest stable development version from GitHub, you can pull this repository and install it using

    ## install.packages("remotes")
    remotes::install_github("valentint/rda")

Of course, if you have already installed `remotes`, you can skip the
first line (I have commented it out).

## Example

This is a basic example which shows you if the package is properly installed:

```{r example}

library(rda)
data(colon)
colon.x <- t(colon.x)
(fit <- rda(colon.x, colon.y))

```
## Community guidelines

### Report issues and request features

If you experience any bugs or issues or if you have any suggestions for additional features, please submit an issue via the [*Issues*](https://github.com/valentint/rda/issues) tab of this repository.  Please have a look at existing issues first to see if your problem or feature request has already been discussed.

### Contribute to the package

If you want to contribute to the package, you can fork this repository and create a pull request after implementing the desired functionality.

### Ask for help

If you need help using the package, or if you are interested in collaborations related to this project, please get in touch with the package maintainer.